### 2018-02-18 doc/manuscript.Rmd
change headings to fit JLR

Corresponding author:

@@

Disclaimers:

Funding support:

Word count: ~4000

@@

Word count: 249 / 250

**Objective**: 
Although elevated serum triacylglyceride (TAG) is a well-described risk factor for
type 2 diabetes (T2DM), few data are available regarding the role of the specific fatty
acid (FA) composition within serum TAG (TAGFA) in the pathogenesis of T2DM. Our aim, therefore, was to
examine longitudinal associations of TAGFA with insulin sensitivity (IS) and
beta-cell function.

**Research Design and Methods**:
We used longitudinal data (3 visits over 6 years) from the Prospective
Metabolism and Islet Cell Evaluation (PROMISE) cohort of adults (n=477) who were at-risk
for diabetes at baseline. Glucose and insulin from an OGTT were used to calculate the outcome variables
Matsuda index (ISI), HOMA2-%S, Insulinogenic Index over HOMA-IR (IGI/IR),
and Insulin Secretion-Sensitivity Index-2 (ISSI-2). Gas chromatography
quantified TAGFA composition. Generalized estimating equations (GEE) adjusted for
confounders and partial least squares (PLS) were used for the analysis.

@@

# Background

@@

# Subjects and Methods

@@

# Acknowledgements

>>>>

Corresponding author contact information:

@@

Running title (max 60 characters):

Abbreviations:

@@

Word count: 249 / 200

**Aims/hypothesis:**
Although elevated serum triacylglyceride (TAG) is a well-described risk factor for
type 2 diabetes (T2DM), few data are available regarding the role of the specific fatty
acid (FA) composition within serum TAG (TAGFA) in the pathogenesis of T2DM. Our aim, therefore, was to
examine longitudinal associations of TAGFA with insulin sensitivity (IS) and
beta-cell function.

**Methods**:
We used longitudinal data (3 visits over 6 years) from the Prospective
Metabolism and Islet Cell Evaluation (PROMISE) cohort of adults (n=477) who were at-risk
for diabetes at baseline. Glucose and insulin from an OGTT were used to calculate the outcome variables
Matsuda index (ISI), HOMA2-%S, Insulinogenic Index over HOMA-IR (IGI/IR),
and Insulin Secretion-Sensitivity Index-2 (ISSI-2). Gas chromatography
quantified TAGFA composition. Generalized estimating equations (GEE) adjusted for
confounders and partial least squares (PLS) were used for the analysis.

@@

# Keywords
<!-- up to 10. Five from list, five free-form. Should not appear in title or
running title -->

# Introduction

@@

# Materials and Methods

@@

# Acknowledgements/grant support
